\documentclass[11pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\begin{document}
\begin{letter}{Hiring Manager \\ Warner Bros}

Dear Hiring Manager,

I am writing to express my enthusiasm for the Machine Learning Engineer position at Warner Bros, as advertised. With a Master of Technology in Aerospace Engineering from the Indian Institute of Science and extensive experience in developing and deploying machine learning models, I am excited about the opportunity to contribute to your innovative team.

In my current role as a Data Scientist at Mercedes-Benz Research and Development India, I have successfully developed and deployed LSTM-based time series models that achieved a 5% reduction in charging time for electric vehicles. This experience has honed my skills in predictive analytics and model evaluation, which I believe aligns perfectly with Warner Bros' need for thorough experimentation and analysis to optimize model performance.

Additionally, my experience in collaborating with data engineers to design and implement robust data pipelines has ensured data quality and consistency across the machine learning lifecycle. I am particularly drawn to Warner Bros' commitment to leveraging the latest advancements in AI/ML, and I am eager to bring my expertise in Python, TensorFlow, and PyTorch to your projects.

I am excited about the possibility of working at Warner Bros and contributing to the development of cutting-edge machine learning solutions. I would welcome the opportunity to discuss how my background, skills, and enthusiasms align with the goals of your team. Thank you for considering my application. I look forward to the possibility of discussing this exciting opportunity with you.

Sincerely,  
Mahendra Gehlot  
\href{mailto:connect.mge@gmail.com}{connect.mge@gmail.com}  
+91-7737101405  
\end{letter}
\end{document}